\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}


\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
\end{flushright}

\vspace{-7pt}

\begin{center}
    \textbf{\Huge \scshape Karan Khandekar} \\ \vspace{8pt}
    \small 
    \faGithub
    \href{github.com/KaranKhandekar1729}{\underline{github.com/KaranKhandekar1729}} $  $
    % \faCode $  $
    % \href{https://www.johndoe.com}
    % {\underline{johndoe.com}} $  $
    \faEnvelope$  $
    \href{mailto:karankhandekar028@gmail.com}
    {\underline{karankhandekar028@gmail.com}}
    \faPhone$  $
    \underline{+919819629531}
    \faLinkedin$  $
    \href{linkedin.com/in/karankhandekar}{\underline{linkedin.com/in/karankhandekar}} $  $
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Patkar Varde College, University of Mumbai}{June 2026}
        {Bachelor of Science in Computer Science}{Current GPA: 9.5/10.0}
  
    \resumeSubheading
      {Patkar Varde College of Science}{April 2022}
      {High School Diploma}{Grade: A}
      
    % \resumeSubheading
    %   {High School \footnotesize{(Dual Enrollment)}}{June 2022}
    %   {}{GPA: 4.0/4.0}

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
    \textbf{Programming Languages}{: Python, Javascript, HTML/CSS} \\
    
    \textbf{Frontend Frameworks}{: Vue.js, React.js} \\
    
    \textbf{Backend Technologies}{: Node.js, Express.js} \\
    
    \textbf{Libraries / Tools}{: Primeflex, Stripe.js, Cloudinary, Parcel.js} \\
    
    \textbf{Database}{: SQL, MongoDB, PocketBase} \\
    
    \textbf{Version Control}{: Git/GitHub} \\
}}
\end{itemize}

% -------------------- EXPERIENCE --------------------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{AI Plans} $|$ \footnotesize\emph{FullStack Developer Intern}}{May 2025 -- July 2025}
\resumeItemListStart
    \resumeItem{Developed \textbf{advanced search functionality} with filtering for research papers, enhancing user navigation and content discovery.}
    \resumeItem{Enhanced user experience for courses by implementing \textbf{markdown support} for authors, code block rendering, and optimizing page \textbf{LCP load times from seconds to milliseconds} through \textbf{Cloudinary integration}, thus improving reading experience.}
    \resumeItem{Redesigned \textbf{review submission interface} to improve overall feel for submitting reviews.}
    \resumeItem{Integrated embedded \textbf{Stripe payment system} with streamlined checkout flow, enabling seamless course purchase transactions and improving user trust.}
    \resumeItem{Built \textbf{responsive web pages} including landing page for AI safety alignment program.}
    \resumeItem{Delivered \textbf{scalable frontend solutions} while collaborating with global stakeholders to meet varied user requirements.}
    \resumeItem{Leveraged continuous \textbf{user feedback} to drive product iterations, implementing \textbf{data-driven improvements} that enhanced platform usability for a wide user base.}
    \resumeItem{\textbf{\textit{Tech Stack: Vue.js, Javascript, Primeflex, Node.js, Express.js, PocketBase, Stripe.js, Cloudinary}}}
\resumeItemListEnd

\resumeSubHeadingListEnd


% -------------------- PROJECTS --------------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://beta.ai-plans.com/events/moonshot-alignment-program}{\underline{Moonshot Alignment Program \faExternalLink}}} $|$ \footnotesize\emph{Vue.js, Javascript, Primeflex}}{}
\resumeItemListStart
    \resumeItem{Designed and developed landing page for AI safety alignment program, optimizing user experience and program accessibility.}
    \resumeItem{Implemented responsive design with interactive elements to enhance user engagement and program accessibility.}
    \resumeItem{Collaborated with program coordinators to ensure technical requirements met educational and engagement goals.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://galacticgateways.vercel.app}{\underline{Space Tourism Web-App \faExternalLink}}} $|$ \footnotesize\emph{React.js, Parcel.js, CSS}}{}
\resumeItemListStart
   \resumeItem{Developed \textbf{interactive content explorer} with detailed information display and enhanced user engagement through immersive presentation.}
   \resumeItem{Implemented \textbf{dynamic package customization system} with personalized selection options based on user preferences.}
   \resumeItem{Built \textbf{end-to-end booking functionality} with ticket reservation system and streamlined user flow.}
   \resumeItem{Designed \textbf{shopping cart interface} with booking management capabilities and clean UI/UX design.}
\resumeItemListEnd

% \resumeProjectHeading
% {\textbf{\href{https://github.com/KaranKhandekar1729/Movie-Ticket-Booking-App}{\underline{Movie Ticket Booking Web App \faExternalLink}}} $|$ \footnotesize\emph{HTML, CSS, Javascript, Bootstrap}}{}
% \resumeItemListStart
%     \resumeItem{Built a movie ticket booking website.}
%     \resumeItem{Fully functional with an interactive design.}
%     \resumeItem{Added feature for ticket generation along with a barcode.}
% \resumeItemListEnd

% \resumeProjectHeading
% {\textbf{\href{https://github.com/KaranKhandekar1729/Quiz-App}{\underline{Quiz App \faExternalLink}}} $|$ \footnotesize\emph{Dart, Flutter}}{}
% \resumeItemListStart
%     \resumeItem{Developed a dynamic Quiz app that allows users to answer multiple-choice questions and receive immediate feedback on their answers.}
%     \resumeItem{Ensured cross-platform compatibility, with the app running seamlessly on both Android and iOS devices.}
% \resumeItemListEnd

\resumeSubHeadingListEnd


% -------------------- EXPERIENCE --------------------
\section{Awards}
  \resumeSubHeadingListStart
        
        \resumeProjectHeading
          {\textbf{ICCSAS '25 - International Conference on Computing, STEM and Applied Sciences
          \footnotesize{}}\vspace{8pt} \footnotesize\emph{}}{March 2025}
          {\small{Won the 'Best Paper Presenter' award at ICCSAS '25: Track 06
          Technology, for my research paper titled 'Quantum Cryptography Algorithms Assessment: A Comprehensive
          Study Using IBM's Qiskit Framework' }}
        % \resumeProjectHeading
        %   {\textbf{President Honor Roll}\vspace{8pt} $|$ \footnotesize\emph{Spring 2024}}{}
        %   {\small{Award of 4.00 GPA in Spring 2024 semester}}
    \resumeSubHeadingListEnd 



\end{document}
